Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-19 paper.tex
Revising the state of the art.
it still has many suggestions and things to address. First thing, it lacks a narrative. The state of the art should be possibly resumed in a sentence, such as
"So far, most forecasting techniques have been based on previous sales. Very few have used, like we do in this paper, pre-sales data. So this is what we are doing here and we will improve methods"

Please @fergunet @amorag @pacastillo take a long hard look at it, and as done before address suggestions and issues and erase them when done.

Sales forecasting is a problem which has been addressed several times
in the literature. Most of the studies have been conducted using
different analysis and forecasting methods, such as regression models
\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy
systems \cite{Mastorocostas2001}, applied to different industrial
sectors. 
% ¿Y qué? Esta frase
% no aporta nada. La primera frase
% tiene que enmarcar el estado del
% arte - JJ
% Antonio - la he intentado mejorar.
% Muchas cosas de la intro tendrían que venir aquí, al estado del
% arte. Habría que reescribir la intro. - JJ

Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this
paper.

In this case, just a few variables are known in advance
\cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
them are categorical, harder to process, even more so if the number
of categories is high. Given these issues, finding adequate
forecasting techniques and selecting  
the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj

>>>>

% Sales forecasting is a problem which has been addressed several times
% in the literature.
% This sentence is useless
In the past, sales prediction has been performed using methods such as  regression models
\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy 
systems \cite{Mastorocostas2001}, applied to different industrial
sectors. 
% ¿Y qué? Esta frase
% no aporta nada. La primera frase
% tiene que enmarcar el estado del
% arte - JJ
% Antonio - la he intentado mejorar.
% Muchas cosas de la intro tendrían que venir aquí, al estado del
% arte. Habría que reescribir la intro. - JJ
% ¿Qué usan esos métodos? - JJ

Specifically, time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
is perhaps the most used technique to tackle the sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this
paper.

In this case, just a few variables are known in advance
\cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
them are categorical, which makes them harder to process, even more so if the number
of categories is high. Given these issues, finding adequate
forecasting techniques and selecting  
the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj
% And it's the 3rd time you cite ChingChin!!! - JJ
